### 2017-06-18 paper.tex
Updating affiliation to follow Lyon university guidelines
Tuning: a comma and a missing word

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Universit\'{e} Jean Monnet / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com \\

@@

Lessons don't maintain themselves.
For technical lessons software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case, what was cutting edge in 2017 may be dated
and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

@@

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that have the usual keywords in their bibliographic entries
and HTML page headers.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Univ Lyon, UJM-Saint-Etienne, F-42023, France / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com \\

@@

Lessons don't maintain themselves.
For technical lessons, software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case, what was cutting edge in 2017 may be dated
and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

@@

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that they have the usual keywords in their bibliographic entries
and HTML page headers.
